HyperLogLog: Exponentially Bad in Adversarial Settings

### 2022-02-05 docs/HLL_exp_bad/main.tex

\begin{table*}[htp]
\caption{Attacks on empty sketches for a classic HLL implementation, averaged over 50 iterations.}
\begin{center}
\begin{tabular}{| l | >{\raggedleft\arraybackslash}p{5em} | >{\raggedleft\arraybackslash}p{5em} | >{\raggedleft\arraybackslash}p{5em} | >{\raggedleft\arraybackslash}p{5em} |}
	\hline
	\textbf{Scenario} &  \multicolumn{2}{c|}{S1} & \multicolumn{1}{c|}{S2} & \multicolumn{1}{c|}{S4}  \\ \hline
	\textbf{Original Card. Est.} & 0 & 0 &  0  & 0   \\ \hline
	\textbf{\# Targeted buckets $B$} & 1 & 128 (= m/2) & 1 &  1 \\ \hline
	\textbf{\# Items added} & 4,132 & 523,791  & 4,106 & 4,106 \\ \hline
	\textbf{Final Card. Est.} & 1 & 177 & 1  & 1 \\ \hline
	\textbf{\# Resets} & 4,718 & 6,973 & - & - \\ \hline
\end{tabular}
\end{center}
\label{table:tab1}
\end{table*}%

@@

\begin{table*}[tb!]
\caption{Comparison of attack results in the S1 adversarial scenario, in the setting of~\cite{hllvuln}.}
\begin{center}
\begin{tabular}{| l | >{\raggedleft\arraybackslash}p{6.8em} | >{\raggedleft\arraybackslash}p{6.8em} | >{\raggedleft\arraybackslash}p{6.8em} |}
    \hline
    \textbf{Attack} & \multicolumn{2}{c|}{Ours} &\multicolumn{1}{c|}{~\cite{hllvuln}} \\ \hline
      \textbf{Original Card. Est.} & 0 & 0 & 0  \\ \hline
       \textbf{\# Targeted buckets $B$} & 1 & 128 (= m/2) & - \\ \hline
     \textbf{\# Items added} & 977 & 125,091 & 74,390 \\ \hline
    \textbf{Final Card. Est.} & 1 & 177 &  15,780 \\ \hline
    \textbf{\# Resets} & 1,148 & 1,655 & 3 \\ \hline

@@

\begin{figure*}[htp]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \caption{Attack results as function of t in the S2 scenario.}
        \includegraphics[width=0.9\textwidth]{figures/graph_S2.pdf}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \caption{Attack results as function of t in the S4 scenario.}
        \includegraphics[width=0.9\textwidth]{figures/graph_S4.pdf} % second figure itself
     \end{minipage}
    \label{fig:graphs}
\end{figure*}

>>>>

\begin{table*}[htp]
\caption{Attacks on empty sketches for a classic HLL implementation, averaged over 50 iterations.}
\begin{center}
\begin{tabular}{| l | >{\raggedleft\arraybackslash}p{5em} | >{\raggedleft\arraybackslash}p{5em} | >{\raggedleft\arraybackslash}p{5em} | >{\raggedleft\arraybackslash}p{5em} |}
	\hline
	\textbf{Scenario} &  \multicolumn{2}{c|}{S1} & \multicolumn{1}{c|}{S2} & \multicolumn{1}{c|}{S4}  \\ \hline
	\textbf{Original Card. Est.} & 0 & 0 &  0  & 0   \\ \hline
	\textbf{\# Targeted buckets $B$} & 1 & 128 ($m/2$) & 1 &  1 \\ \hline
	\textbf{\# Items added} & 4,132 & 523,791  & 4,106 & 4,106 \\ \hline
	\textbf{Final Card. Est.} & 1 & 177 & 1  & 1 \\ \hline
	\textbf{\# Resets} & 4,718 & 6,973 & - & - \\ \hline
\end{tabular}
\end{center}
\label{table:tab1}
\end{table*}%

@@

\begin{table*}[tb!]
\caption{Comparison of attack results in the S1 adversarial scenario, in the setting of~\cite{hllvuln}.}
\begin{center}
\begin{tabular}{| l | >{\raggedleft\arraybackslash}p{6.8em} | >{\raggedleft\arraybackslash}p{6.8em} | >{\raggedleft\arraybackslash}p{6.8em} |}
    \hline
    \textbf{Attack} & \multicolumn{2}{c|}{Ours} &\multicolumn{1}{c|}{~\cite{hllvuln}} \\ \hline
      \textbf{Original Card. Est.} & 0 & 0 & 0  \\ \hline
       \textbf{\# Targeted buckets $B$} & 1 & 128 ($m/2$) & - \\ \hline
     \textbf{\# Items added} & 977 & 125,091 & 74,390 \\ \hline
    \textbf{Final Card. Est.} & 1 & 177 &  15,780 \\ \hline
    \textbf{\# Resets} & 1,148 & 1,655 & 3 \\ \hline

@@

\begin{figure*}[htp]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \caption{Attack results as function of t in scenario S2 with initially non-empty HLL sketch.}
        \includegraphics[width=0.9\textwidth]{figures/graph_S2.pdf}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \caption{Attack results as function of t in scenario S4 with initially non-empty HLL sketch.}
        \includegraphics[width=0.9\textwidth]{figures/graph_S4.pdf} % second figure itself
     \end{minipage}
    \label{fig:graphs}
\end{figure*}
